Mahotas: Open source software for scriptable computer vision

### 2012-08-11 paper.tex
MIN A note about version numbers

\subsection{Functionality and Interface}

@@

\subsection{Implementation}

>>>>

Version 1.0 has been released recently and this is now a mature, well-tested
package (the first version was made available over 4~years ago). \footnote{Note
for reviewers: the version currently available implements all functionality
described in this manuscript. I will release it as version 1.0 when this
manuscript is accepted. Naturally, any bugs that are reported in the
meanwhile will be addressed.}

\section{Functionality and Interface}

@@

\section{Implementation}
